Millions of Type Errors

### 2023-03-24 oopsla23/paper.tex
Add screenshots

\documentclass[
  acmsmall,
  review,
  anonymous,
]{acmart}

@@

\section{Roblox Contex}

>>>>

\documentclass[
  acmsmall,
  review,
%  anonymous,
]{acmart}

@@

\section{\anon{Roblox} Context}

\begin{figure}
  \anon{
    \includegraphics[width=.45\textwidth]{img/roblox-studio.png}
    \includegraphics[width=.45\textwidth]{img/roblox-studio-ide.png}
  }
  \caption{\anon{Roblox Studio 3D creation} tools (left) and IDE (right)}
  \label{fig:roblox-studio}
\end{figure}

Creators of \anon{Roblox experiences} use \anon{Roblox Studio},
which combines \anon{3D creation} tools as well as an Integrated
Developer Environment (IDE), as seen in Fig.~\ref{fig:roblox-studio}.
